The pollination trade-off

### 2018-12-08 paper/manuscript.Rmd
Third and fourth paragraph of discussion: abundance and visit effectiv

\R{disc-facil-comp}Both of the tests used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community. 
Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood. 
Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.  
* We did find a trade-off between the number of partners a species interacts with and the mutualistic service. Interacting with more species alone is often accompanied by a decreases in both the quantity and quality of pollination. 
* However, the effect and importance of this trade-off is comparatively small when considering other factors that describe the species niche and its ecological settings. 
* We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any. This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their own pollen gets deposited on the stigma. Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favours cross-pollination as, evolutionary, it has been shown to be a better strategy than cloning. 
* Overall it seems like density seems to be a dominant force behind pollen transfer. If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is reflected in a smaller amount of deposited pollen. We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen. 
* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentally related to the way we understand and mathematically represent mutualistic systems. 
Some of the most widely used theoretical models of pollination account for the negative effects of mutualism by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree. 
This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
However we show that care must be taken because the negative effects of the mutualistic trade-off in both the quantity and quality of pollination can be offset by density mechanisms. Species with large degrees also tend be abundant and prolific pollen producers.

>>>>

\R{disc-facil-comp}Both of the tests used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community. 
Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood. 
Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.

These trade-offs were most evident precisely in the strategies that most strongly modulate pollen deposition. 
We found that the strategies that increased the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
Adopting a strategy of high visitation increasses the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen. 
Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen.

Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained. 
Simultaneously, because visitation, pollen production and abundance are correlated, these trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between these factors to increasse conspecific pollen and reduce heterospecific pollen deposition. 
The relative wide range of in our model coefficients might be explained by the wide variation of the extent to which plant species are affected by pollen deposition. 
While some species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985]. 
* We did find a trade-off between the number of partners a species interacts with and the mutualistic service. Interacting with more species alone is often accompanied by a decreases in both the quantity and quality of pollination. 
* However, the effect and importance of this trade-off is comparatively small when considering other factors that describe the species niche and its ecological settings. 
* We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any. This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their own pollen gets deposited on the stigma. Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favours cross-pollination as, evolutionary, it has been shown to be a better strategy than cloning. 
* Overall it seems like density seems to be a dominant force behind pollen transfer. If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is reflected in a smaller amount of deposited pollen. We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen. 
* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentally related to the way we understand and mathematically represent mutualistic systems. 
Some of the most widely used theoretical models of pollination account for the negative effects of mutualism by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree. 
This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
However we show that care must be taken because the negative effects of the mutualistic trade-off in both the quantity and quality of pollination can be offset by density mechanisms. Species with large degrees also tend be abundant and prolific pollen producers.
